---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  fig.width = 12,    # increase width
  fig.height = 8,    # optional: increase height
  out.width = "100%",
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```


# paRks

<!-- badges: start -->

<!-- badges: end -->

paRks is a package that allows you to find different types of recreational spaces. You can input your address or your location and select whether you want to find the nearest or largest green or blue space. Using paRks you can then generate a map showing you the route to take to your selected space. paRks is colorblind friendly and includes color support for deuteranopia, protanopia as well as tritanopia.

## Installation

You can install the development version of paRks like so:

``` r
library(devtools)
install_github("Miner501/paRks")
```

## Example

The first step of using paRks is to geocode an address or a set of lat/lon coordinates.

```{r example}
library(paRks)

location <- geocode_address("Kiliansplatz, Wuerzburg")

```

Once an address or location has been geocoded, you can input the maximum distance you are willing to travel to find an adequate blue or green space.

```{r zone}

zone <- travel_zone(location, distance_km = 5)

```

Once the zone has been calculated based on OSM routing information you must fetch the blue and green spaces of within the zone as well as the road network. The road network is useful to make the final map more visually pleasing.

```{r fetching}
greens <- get_greenspaces(zone, mode = "standard") # mode can also be set to "broad" to include any type of green space, even ones that may not be publicly accessible.

blues  <- get_bluespaces(zone)

roads  <- get_roads(zone)
```

At this point you can now start navigating. You can select if you would like to be navigated to a green or blue space. If selecting a green space you also have the choice between the largest and closest.

```{r navigation}
result <- navigate_to_target(
  location = location,
  zone = zone,
  greens = greens,
  blues = blues,
  target_type = "green",     # or "blue"
  preference = "largest"     # or "largest"
)
```

Finally we can plot our results on a map.

```{r mapping}
plot_travel_map_gg(
  zone = zone,
  greens = greens,
  blues = blues,
  roads = roads,
  route = result$route,
  route_distance = result$length_m,
  start_location = location,
  target_type = "green",  # or "blue"
  palette = "normal" #this is where you can select if you have any form of colorblindness mentioned earlier in the Readme
)
```
