---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  fig.width = 12,    # increase width
  fig.height = 8,    # optional: increase height
  out.width = "100%",
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# paRks

<!-- badges: start -->

<!-- badges: end -->

paRks is a package that allows you to find different types of recreational spaces. You can input your address or your location and select whether you want to find the nearest or largest green or blue space. Using paRks you can then generate a map showing you the route to take to your selected space. paRks is colorblind friendly and includes color support for deuteranopia, protanopia as well as tritanopia.

## Installation

You can install the development version of paRks like so:

``` r
library(devtools)
install_github("Miner501/paRks")
```

## Package Functions

| **Function Name** | **Description** |
|---------------------|-------------------------------------------------|
| geocode_address(address) | Uses the `tidygeocoder` package and the Nominatim API to convert a street address into latitude and longitude coordinates. |
| geocode_coords(lat, lon) | Creates a tibble from latitude and longitude values to represent a geographic point. |
| travel_zone(location, distance_km) | Generates a polygon travel zone either using a circular buffer for short distances or OSRM-based isochrones for longer travel ranges. |
| FloodMap() | Create a map displaying calculated flood areas based on date or by flood size. |
| get_greenspaces(zone, mode, min_area_ha) | Downloads and filters OpenStreetMap green features (like parks and forests) within a specified travel zone. |
| get_bluespaces(zone) | Retrieves water-related features (like rivers, lakes, and wetlands) from OpenStreetMap within a travel zone. |
| get_roads(zone) | Fetches road network features that intersect with a specified travel zone from OpenStreetMap. |
| navigate_to_target(location, zone, greens, blues, target_type, preference) | Selects the best green or blue space based on user preference (closest or largest) and computes a route to it using OSRM. |
| plot_travel_map_gg(...) | Uses `ggplot2` and `sf` to create a detailed map showing green/blue spaces, roads, a travel zone, and a route from a starting point. |

## Example

The first step of using paRks is to geocode an address or a set of lat/lon coordinates.

```{r example}
library(paRks)

location <- geocode_address("Kiliansplatz, Wuerzburg")

```

Once an address or location has been geocoded, you can input the maximum distance you are willing to travel to find an adequate blue or green space.

```{r zone}

zone <- travel_zone(location, distance_km = 5)

```

Once the zone has been calculated based on OSM routing information you must fetch the blue and green spaces of within the zone as well as the road network. The road network is useful to make the final map more visually pleasing.

```{r fetching}
greens <- get_greenspaces(zone, mode = "standard") # mode can also be set to "broad" to include any type of green space, even ones that may not be publicly accessible. You can also set the minimum size by using min_area_hea = 2 etc..

blues  <- get_bluespaces(zone)

roads  <- get_roads(zone)
```

At this point you can now start navigating. You can select if you would like to be navigated to a green or blue space. If selecting a green space you also have the choice between the largest and closest.

```{r navigation}
result <- navigate_to_target(
  location = location,
  zone = zone,
  greens = greens,
  blues = blues,
  target_type = "green",     # or "blue"
  preference = "largest"     # or "closest"
)
```

Finally we can plot our results on a map.

```{r mapping}
plot_travel_map_gg(
  zone = zone,
  greens = greens,
  blues = blues,
  roads = roads,
  route = result$route,
  route_distance = result$length_m,
  start_location = location,
  target_type = "green",  # or "blue"
  palette = "normal", #this is where you can select if you have any form of colorblindness mentioned earlier in the Readme
  title = "Example Map of paRks"
)
```

## Limitations

The way the OSRM package is structured only allows for car based routing. This means that the route it suggests you to take, may not be the shortest or most realistic one. Additionally, because OSM is a community project, there are some small issues in the road-network. This may cause there to be "islands" within the zone that are shown as being inaccessible, even though in actuality they are perfectly accessible. An example of this is shown in the plot above, where one of these "islands of inaccessibility" is located just north of the large blue space. Additionally OSRM struggles with routing for very short distances, causing the travel zone calculation to become buggy, if the distance to be calculated is less than 2 km. These are known bugs, for which there is currently no available simple fix. In the future it may be possible to create an own API for OSM-based routing that includes walking, or cycling.
